---
title: "ProjectMarkdown"
output:
  word_document: default
  html_document: default
date: "2022-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Profile

```{r}
ID = 202249724
source('XYZprofile.r')
XYZprofile(ID)
```

#### Importing libraries

```{r}
library(readODS)
library(dplyr)
library(ggpubr)
library(ggplot2)
library(tidyverse)
library(CatEncoders)
```

## Cleaning and wrangling the data

```{r}
datall = read.ods(file = 'dvsa1203.ods')
dat = datall[2:16] #The first sheet contains content and metadata.
```

Looping through our list of dataframe,

```{r}
cleaned_data = list()
for (i in 1:length(dat)) {
    
    cleaned_data[[i]] <- dat[[i]][-(1:7),] 
    #Removing metadata; {first 6 rows and the column names(we will assign new ones later)}
    if (i > 7){ #Removing empty columns in some sheets and fixing their column names
        cleaned_data[[i]] <- cleaned_data[[i]][-c(6,10)]
        colnames(cleaned_data[[i]]) = colnames(cleaned_data[[1]])}
}
```

Binding all of the dataframes in the above list in one, and assigning column names

```{r}
full_data = bind_rows(cleaned_data, .id = 'Year', )
colnames(full_data) = c('Year','Centre','Age','Conducted_Male','Passes_Male','Pass_Rate_Male',
             'Conducted_Female','Passes_Female','Pass_Rate_Female',
             'Conducted_Total','Passes_Total','Pass_Rate_Total')
```

Re-encoding missing values of centres

```{r}
full_data$Centre[which(full_data$Centre == "",arr.ind = TRUE)] <- NA
full_data <- full_data %>% fill(Centre, .direction = 'down')
```

```{r}
full_data[which(full_data == "..",arr.ind = TRUE)] <- NA
```

Re-encoding the years

```{r}
for (i in 1:15) {
    full_data$Year[which(full_data$Year == i,arr.ind = TRUE)] <- 2006 + i}
```
## Exploring the Data

```{r}
Passrates <- as.numeric(full_data$Pass_Rate_Male)
mean(Passrates,na.rm = TRUE);sd(Passrates,na.rm = TRUE)
```


```{r, figures-side, fig.show="hold", out.width="50%"}
par(mar = c(4, 4, .1, .1))
ggplot(data.frame(Passrates), aes(x=Passrates)) +
geom_histogram(aes(y = after_stat(density)), col="paleturquoise",na.rm = TRUE) +
ggtitle("Density plot of Pass Rates") + xlab("Passing Rates") + stat_function(fun = dnorm, args = list(mean = mean(Passrates,na.rm = TRUE), sd = sd(Passrates,na.rm = TRUE)), lwd=1.5, col="brown1")
ggqqplot(Passrates)
```


```{r}

```


Function for getting data of specific city

```{r}
specity <- function(city){
    citydata <- data.frame()
    
    x <- which(full_data== city,arr.ind = TRUE)
    p <- full_data[x[,1],]
    citydata <- rbind(citydata,p)
    rownames(citydata) <- NULL
    citydata <- citydata[citydata$Centre == city,]
    citydata <- citydata[!(citydata$Age == 'Total' | citydata$Age == ''),]
    return(citydata)
}
```

```{r}
nearLSE <- specity('Wood Green (London)')
```
We see that data is missing for years past 9, as city name is different being Wood Green. So, we will combine this data too.

```{r}
extra <- specity('Wood Green')
nearLSE <- rbind(nearLSE,extra)
```


```{r}
nearhome <- specity('Nottingham (Colwick)')
```


Function to get data for specific Age

```{r}
specage <- function(df,age){
    agedata <- data.frame()
    x <- which(df$Age== age,arr.ind = TRUE)
    p <- df[x,]
    agedata <- rbind(agedata,p)
    rownames(agedata) <- NULL
    return(agedata)
}
```

```{r}
LSEaged <- specage(nearLSE,25)
```


```{r}
homeaged <- specage(nearhome,25)
```
```{r}
library(writexl)
write_xlsx(homeaged,'Nottinghamaged.xlsx')
write_xlsx(LSEaged,'LSEaged.xlsx')
write_xlsx(nearhome,'Nottingham.xlsx')
write_xlsx(nearLSE,'LSE.xlsx')

```

```{r}
write_xlsx(full_data,'full_data.xlsx')
```


```{r}
library(nortest)
ad.test(Passrates)
ks.test(Passrates,'pnorm')
```


```{r}
numhome <- data.frame(sapply(nearhome, function(x) as.numeric(as.character(x))))
```
```{r}
numhome['Centre'] <- rep(1,nrow(numhome))

```

```{r}
male <- numhome[,c(1,2,3,5)]
                                                                                                                                
duplicate <- function(year,centre,age,response){
    expanded <- 1:response
    repeated <- data.frame('Year' = year,'Centre' = centre, 'Age' = age,'pass_fail' = expanded)
}
expanded_rows <- Map(f = duplicate,male$Year, male$Centre, male$Age,male$Passes_Male)
maled <- do.call(rbind,expanded_rows)
```

```{r}
maled$pass_fail <- rep(1,length(maled$pass_fail))
```
```{r}
malefail <- numhome[,c(1,2,3)]
malefail['Fails_male'] <- numhome$Conducted_Male - numhome$Passes_Male
```
```{r}
fexpanded_rows <- Map(f = duplicate,malefail$Year,malefail$Centre,malefail$Age,malefail$Fails_male)
malefailed <- do.call(rbind,fexpanded_rows)
malefailed$pass_fail <- rep(0,length(malefailed$pass_fail))
```
```{r}
homelogistic <- rbind(maled,malefailed)
```
```{r}
numlse <- data.frame(sapply(nearLSE, function(x) as.numeric(as.character(x))))

numlse['Centre'] <- rep(0,nrow(numlse))

lsepasses <- numlse[,c(1,2,3,5)]
lsexpanded <-  Map(f = duplicate,lsepasses$Year,lsepasses$Centre,lsepasses$Age,lsepasses$Passes_Male)
lsepassed <- do.call(rbind,lsexpanded)
lsepassed['pass_fail'] <- rep(1,nrow(lsepassed))
```

```{r}
lsefails <- numlse[,c(1,2,3)]
lsefails['pass_fail'] <- numlse$Conducted_Male - numlse$Passes_Male

lsefexpanded <- Map(f = duplicate,lsefails$Year,lsefails$Centre,lsefails$Age,lsefails$pass_fail) 
lsefailed <- do.call(rbind,lsefexpanded)
lsefailed$pass_fail <- rep(0,nrow(lsefailed))
```
```{r}
lselogistic <- rbind(lsepassed, lsefailed)
```

```{r}
logisticdat = rbind(homelogistic,lselogistic)
```

To adjust for the high value of years affecting the model, we will encode the Years as 1,2,.....15
```{r}
logisticdat$Year <- as.numeric(factor(logisticdat$Year))
```





```{r}
model <- glm(pass_fail~.,data = logisticdat)
```

```{r}
summary(model)
```

We can compute a chi-square statistic to test if a model is useful.
Chi-Sq statistic : 15013 - 14916 = 97 for 60060 - 60057 = 3 dof

```{r}
test <- function(age,year,centre){
    Age <- c(age);Year <- c(year);Centre <- c(centre)
    test <- data.frame(Year,Age,Centre)
    return(test)}
```

```{r}
c(predict.glm(model,test(25,16,1),se.fit = TRUE),predict.glm(model,test(25,16,0),se.fit = TRUE))
```


```{r}
library(rms)
lrm(pass_fail~.,data = logisticdat)
```

```{r}
library(ggplot2)
lseagednum <- data.frame(sapply(LSEaged, function(x) as.numeric(as.character(x))))
homeagednum <- data.frame(sapply(homeaged, function(x) as.numeric(as.character(x))))
```


```{r}
ggplot(data = lseagednum,aes(Year,Pass_Rate_Male, col = 'LSE')) +  geom_point() + geom_line() + geom_point(data = homeagednum, aes(Year,Pass_Rate_Male,col = 'Nottingham (Colwick)')) + geom_line(data = homeagednum,aes(Year,Pass_Rate_Male,col = 'Nottingham (Colwick)'))
```

## Permutation test

```{r}
set.seed(1111)
x <- as.numeric(homeaged$Pass_Rate_Male)
y <- as.numeric(LSEaged$Pass_Rate_Male)
z <- c(x,y)
stat <- abs(mean(x) - mean(y)) 
k <- 0
for (i in 1:10000) {
    zperm <- sample(z,29)
    statperm <- abs(mean(zperm[1:14])-mean(zperm[15:29])) 
    if (statperm > stat) k <- k+1}
```

```{r}
pval <- k/10000
pval
```


```{r}

```

